\section*{\centering Reproducibility Summary}

\subsubsection*{Scope of Reproducibility}
This paper introduces a new architecture for sarcasm detection leveraging multimodal information from text and images. The authors claim that their model outperforms the state-of-the-art models on the Multimodal Sarcasm Detection dataset. With this work, we aim to reproduce these results and confirm or deny the authors' claims.

\subsubsection*{Methodology}
Our reproducibility study was performed starting from the code provided by the authors, with minimal changes. We used the same dataset, evaluation metrics and model hyperparameters as the original paper. We used a Colab notebook to run the experiments on an NVIDIA V100 GPU.

\subsubsection*{Results}
We were able to confirm the results reported in the paper to within 1.4\% F1 score and 0.1\% accuracy, therefore supporting the claim that the proposed model outperforms the state-of-the-art models on the Multimodal Sarcasm Detection dataset. 

\subsubsection*{What was difficult}
The setup of the experiment required some adjustments concerning the version of the required libraries. We also needed to fix some minor bugs in the code and perform some preprocessing operations locally. 

\subsubsection*{What was easy}
After the setup of the experiment was completed, running the code and reproducing the results stated in the paper was pretty straightforward.

\subsubsection*{Communication with original authors}
No communication with the original authors was necessary.
